---
title: "MA677-G&S311"
author: "ChenxunLi"
date: "2/10/2021"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

## Explain why m between 69-73

```{r}
###Build a function to plot power curve
Power_Cirve <- function(n,m,p_origin){
  
  p <- seq(p_origin,1,1/n)
  
  for (i in 1:length(m)){
  ###make the first part of the datasets
  if (i == 1){
    k=0
    for(j in m[1]:100){
   ##use dbinom() to provide the probability density distribution of each point
    k=k+dbinom(j,n,p)
     dt <- data.frame(p, Critical_Value=paste('m=',m[i],sep=''),k)
    }
  }
    ###use rbind() to make the left part of datasets
  else{
    k=0
    for(j in m[i]:100){
    k=k+dbinom(j,n,p)
    
    }
    dt <- rbind(dt,data.frame(p, Critical_Value=paste('m=',m[i],sep=''),k))
  }
}

 ##plot the power curve 
ggplot()+
  geom_rect(aes(xmin = 0.6, xmax = 0.8, ymin = 0.05, ymax = 0.95), alpha = 0.5)+
  geom_line(aes(p, k, color = Critical_Value), dt)+
  labs(y=NULL,title = 'Power curves with different Critical Value')
}


Power_Cirve(100,c(50,60,69,70,73,80,90),0.4)

```
The x of gray rectangle represents the p of old drug is 0.6 and the p of new drug is 0.8. And the y of gray rectangle represents the critical number m can make each of these undesirable cases less than 5 percent probable.

As we can see, with increase of m, the curve will move to the right, and we can find that the curve which represents that critical value m is 69 crosses with the left bottom of the rectangle, which means that the probability of type 1 mistake is 5%. Also,the curve which represents that critical value m is 73 crosses with the right top of the rectangle, which means that the probability of type 2 mistake is 5%(1-95%).


## Show the Figure 3.7

```{r}
Power_Cirve(100,c(69,73),0.4)

```

